\documentclass{standalone}
% preamble: usepackage, etc.
\begin{document}

\thesisacknowledgement
First and foremost, I want to express my gratitude to my supervisor, Professor Jian Ping Li, who transformed me into a successful researcher through his patience, advice, and rigorous tutoring. Your prompt suggestions and counsel guided me in the right route, allowing me to achieve my PhD ambitions. I appreciate your confidence in me and the pleasant relationship you established with me during my academic years. I have learned a great deal from you, not only in terms of academics, but also in terms of overall development.

My research partner, Grace Ugochi Nneji, has been a huge source of inspiration for me over the last few years. Your regular motivation, interactions, and remarks influenced the direction of my studies and pushed me to achieve more. Your contributions were important elements of my foundation. It has also been a great pleasure to work with my Wavelet Analysis and Active Media Technology and Big Data Research Lab colleagues. Your suggestions and participation have helped to make my journey memorable and productive.

In addition, I owe a debt of appreciation to certain friends who have had a significant impact on my life. This includes Ariyo Oluwasanmi, Folarin Mordecai Raji, and Akeem Shokanbi. Your wishes, support, and care created an environment that was positive and conducive to my mental and physical health. Thank you for being such a wonderful people.

Thank you to UESTC's International Student Education Office and the entire School of Computer Science and Engineering. Finally, I would like to offer my heartfelt appreciation to my family for their unwavering support. During the difficult moments, I find consolation in your love and wishes. I owe everything I am to my late mother who was always willing to help me become the man of my dream.


\end{document}